\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/background.tex

Refraction networking operates by injecting covert communication inside a
client's HTTPS connection with a reachable site, also known as a decoy site. In
a regular HTTPS session, a client establishes a TCP connection, performs a TLS
handshake with a destination site, sends an encrypted web request, and
receives an encrypted response. In refraction routing, at least one direction
of this exchange is observed by a \emph{refraction station} (RS), deployed at
some Internet service provider (ISP). The RS watches for a covert signal from
the client that this connection is to be used for censorship circumvention.
Upon seeing the signal, the RS will take over the HTTPS session,
and establish a proxy session with the client that can then be used for covert
communication.

@@

One of the key challenges for refraction networking is in taking over a session. The RS must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client. A simple approach is to have the refraction station act as an inline transparent proxy (\cref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site. After a TLS handshake has been completed, the RS terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.

@@

TapDance~\cite{tapdance14} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (\cref{fig:tapdance}). In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the RS takes over the connection in its place. After a client would receive a packet initiated by the RS, its TCP sequence numbers would become desynchronized with the decoy site, causing the decoy to ignore the packets sent by the client.

This approach reduced the barriers to deployment and TapDance was used in production during a pilot study, serving upwards of 50\,000 real-world users~\cite{frolov2017isp}. \nikita{worth mentioning that it's being used in production again? we don't have a public ref for that though.} The tap-based approach, however, has some disadvantages. A decoy site will only ignore packets as long as the sequence numbers stay within its TCP window, and will terminate the connection after a timeout. Frolov et al.\ report that in their pilot, they eliminated roughly a third of potential decoy sites due to their measured window or timeout values being too small~\cite{frolov2017isp}. Even so, sessions that try to upload non-trivial data amounts (in excess of about 15\,KB) or last longer than the timeout value (ranging from 30--120\,s) require the user to create new refraction connections, adding overhead, complexity, and opportunities for errors. Additionally, keeping the connections to the decoy site open for tens of seconds uses up the site's resources; Frolov et al.\ found that a default configuration of the Apache web server would only keep 150 simultaneous connections open, while pilot deployment would often result in dozens of connections to the same decoy site, creating a scaling concern.

\scheme is able to avoid these problems by splitting up the traffic between a registration session and a dark session \nikita{are these good terms?} (\cref{fig:dark-decoys}). The registration session is used to send a signal to the RS to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference. The dark session connects to a dark address that is not routed to any host; the RS instead acts as a remote endpoint for the entirety of the connection, starting with the TCP handshake. This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in \cref{XXX}.

\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the RS to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}. In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.

>>>>

Refraction networking operates by injecting covert communication inside a
client's HTTPS connection with a reachable site, also known as a decoy site. In
a regular HTTPS session, a client establishes a TCP connection, performs a TLS
handshake with a destination site, sends an encrypted web request, and
receives an encrypted response. In refraction routing, at least one direction
of this exchange is observed by a \emph{refraction station}, deployed at
some Internet service provider (ISP). The station watches for a covert signal from
the client that this connection is to be used for censorship circumvention.
Upon seeing the signal, the station will take over the HTTPS session,
and establish a proxy session with the client that can then be used for covert
communication.

@@

One of the key challenges for refraction networking is in taking over a session. The station must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client. A simple approach is to have the refraction station act as an inline transparent proxy (\cref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site. After a TLS handshake has been completed, the station terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.

@@

TapDance~\cite{tapdance14} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (\cref{fig:tapdance}). In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the station takes over the connection in its place. After a client would receive a packet initiated by the station, its TCP sequence numbers would become desynchronized with the decoy site, causing the decoy to ignore the packets sent by the client.

This approach reduced the barriers to deployment and TapDance was used in production during a pilot study, serving upwards of 50\,000 real-world users~\cite{frolov2017isp}. 
%\nikita{worth mentioning that it's being used in production again? we don't have a public ref for that though.} 
The tap-based approach, however, has some disadvantages. A decoy site will only ignore packets as long as the sequence numbers stay within its TCP window, and will terminate the connection after a timeout. Frolov et al.\ report that in their pilot, they eliminated roughly a third of potential decoy sites due to their measured window or timeout values being too small~\cite{frolov2017isp}. Even so, sessions that try to upload non-trivial data amounts (in excess of about 15\,KB) or last longer than the timeout value (ranging from 20--120\,s) require the user to create new refraction connections, adding overhead, complexity, and opportunities for errors. Additionally, keeping the connections to the decoy site open for tens of seconds uses up the site's resources; Frolov et al.\ found that a default configuration of the Apache web server would only keep 150 simultaneous connections open, while the pilot deployment would often result in dozens of connections to the same decoy site, creating a scaling concern.

\scheme is able to avoid these problems by creating proxies at unused IP addresses, allowing the station full control over a host it has created, rather than forcing it to mimic an already existing decoy (\cref{fig:dark-decoys}).
%The registration session is used to send a signal to the station to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference. The dark session connects to a dark address that is not routed to any host; the RS instead acts as a remote endpoint for the entirety of the connection, starting with the TCP handshake. 
This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in Section~\ref{sec:attacks}.

\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the station to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}. In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.

### 2019-02-16 paper/related.tex

TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
decoy into staying silent, and allowing the station to respond instead. However,
as previously described, this trick comes at a cost: the decoy only stays silent
for a short timeout (typically 30-120 seconds), and limits the amount of data
the client can send before it responds. TapDance clients must keep connections
short and repeatedly reconnect to decoys, increasing overhead and potentially
alerting censors with this pattern. \scheme addresses this issue and allows
clients to maintain long-lived connections to the dark decoy.

@@

Slitheen~\cite{slitheen16} focuses on addressing observability by replacing
data in packets sent by the legitimate decoy. Thus, even the packet timings and
sizes of a Slitheen connection match that of a legitimate decoy connection.
However, Slitheen also requires inline-blocking, and introduces a large overhead
as it has to wait for the subset of data-carrying packets from the decoy that
Slitheen can safely replace. We note that the Slitheen model of mimicry is
compatible with \scheme, as we could use Slitheen as the application
protocol. Despite using a passive tap, our scheme is effectively inline to the
dark decoy (which won't otherwise respond).

@@

\scheme allow a large amount of flexibility compared to previous schemes.
Because we have significant degrees of freedom in choosing the specific
application the dark decoy will mimic or talk, our scheme can combine the best
of existing Refraction Networking protocols to achieve high performance, be easy
to deploy, and
also be resistant to active attacks such as replaying or probing by the censor.
Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
their features, as compared to \scheme.

>>>>

TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
decoy into staying silent, and allowing the station to respond instead. However,
as previously described, this trick comes at a cost: the decoy only stays silent
for a short timeout (typically 30-120 seconds), and limits the amount of data
the client can send before it responds. TapDance clients must keep connections
short and repeatedly reconnect to decoys, increasing overhead and potentially
alerting censors with this pattern. \scheme addresses this issue and allows
clients to maintain long-lived connections to the phantom host.

@@

Slitheen~\cite{slitheen16} focuses on addressing observability by replacing
data in packets sent by the legitimate decoy. Thus, even the packet timings and
sizes of a Slitheen connection match that of a legitimate decoy connection.
However, Slitheen also requires inline-blocking, and introduces a large overhead
as it has to wait for the subset of data-carrying packets from the decoy that
Slitheen can safely replace. We note that the Slitheen model of mimicry is
compatible with \scheme, as we could use Slitheen as the application
protocol. Despite using a passive tap, our scheme is effectively inline to the
phantom host (which won't otherwise respond).

@@

\scheme allow a large amount of flexibility compared to previous schemes.
Because we have significant degrees of freedom in choosing the specific
application the phantom host will mimic or talk, our scheme can combine the best
of existing Refraction Networking protocols to achieve high performance, be easy
to deploy, and
also be resistant to active attacks such as replaying or probing by the censor.
Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
their features, as compared to \scheme.
